Species richness and network structure jointly drive total biomass and its temporal stability in fish communities

### 2020-09-15 manuscript/bef_stability/manuscript.Rmd
Review by elisa + put CV/synchrony comparison

- Number of words:
  - Abstract: 142 
  - Main text: 4929

@@

---
#Our aim was to evaluate the effects of the network structure on the total
#biomass and its temporal stability in natural communities, which have been
#poorly documented. To do so, we quantified the effects, directs and indirects,
#of habitat properties, species richness, and food web structure, on the total biomass
#and stability of fish communities, from the ONEMA fish dataset, across 99
#locations in France from 1995 to
#2018. We infered trophic interactions networks based on body size-dependency in
#food diet from the literature and prey/predator body size ratio for piscivory ^[
#We inferred trophic networks at the scale of trophic
#species (i.e. nodes being body size classes) to take in account ontogenic diet
#shifts and that fish-fish trophic interaction depends on body size ratio between
#prey and predator. On the other side, the community metrics were defined at the
#species level, (i.e.  species richness, average species CV and synchrony).  ].
#We built structural equation models to disantangle the direct and indirect
#effects of environmental drivers, species richness and network structure on both
#total biomass and biomass stability.  
---

Species richness and network structure are at the basis of the predictions of
total biomass, productivity and stability. However, empirical data linking
network structure and ecosystem properties are lacking. We used a dataset of
standardized fish sampling in French streams running from 1995
to 2018. We inferred trophic interactions thanks to recorded body size and diet
literature. We investigated the direct and indirect effects of stream size
and temperature, species richness and network structure on total biomass and its
temporal stability. Species richness and average trophic level had
a positive relationship with total biomass while they had respectively a
negative and positive effect on temporal stability. We found a strong link
between species richness and network structure, highlighting that their effects
should be assessed conjointly. Overall, our study opens fruitful perspectives on
the link between species richness, network structure and ecosystem properties.

@@

Species richness promotes higher biomass production in a variety of ecosystems
and taxons. Indeed species richness generally increases primary productivity
and total biomass in experimental plant communities [@tilman_productivity_1996;
@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016], but also in briophyte communities
[@mulder_physical_2001], stream feeders [@cardinale_species_2002] and aquatic
bacterial consumers [@pennekamp_biodiversity_2018]. Theoretical models also
predict this pattern in plant communities [@tilman_plant_1997;
@loreau_partitioning_2001] and food webs [@schneider_animal_2016]. Resource use
complementarity and selection effects have been proposed to elucidate the
positive effect of species richness on productivity. The complementarity in
resource use, rising through niche differentiation and interspecific
facilitation, increase the total amount of resource used
[@loreau_biodiversity_1998; @cardinale_species_2002; @loreau_partitioning_2001].
A positive selection effect arises when species richness leads to an higher dominance
of the most productive species [@tilman_plant_1997; @loreau_partitioning_2001].

In contrast, positive [@wu_relationship_2015; @li_relationship_2018],
negative or non significant effects of species richness on total biomass have been found
in natural forests [@szwagrzyk_above-ground_2007; @jacob_productivity_2010;
@seidel_relationship_2013]. Some authors suggest that the lack of resource
complementarity or environmental harshness might be responsible for an absence or a
negative effect of species richness [@loreau_partitioning_2001; @he_global_2013;
@wu_relationship_2015]. Overall, under what conditions and through what
mechanisms we should observe positive relationships between biomass and species
richness in natural settings remains an open question.

Many studies showed that species richness also increases temporal stability of
communities,
i.e. variation through time, often quantified by the temporal CV. Such positive
relationships between species richness and temporal stability have been reported
in experimental grasslands and aquatic bacterial systems
[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018]. Theoretical works
have clarified which mechanisms generate this positive relationship between
species richness and temporal stability [@loreau_species_2008;
@thibaut_understanding_2013], (1) species synchrony and (2) species variability. Species
synchrony quantify to what extent the fluctuations of abundances or biomasses
through time are correlated among species. A low synchrony in species
fluctuations, i.e.  asynchrony, is synonymous of compensatory dynamic, where the
decrease in abundance of a species is compensated by the increase of an other.
Asynchrony is generally the main mechanism whereby species richness has a
stabilizing effect on temporal stability [@tilman_biodiversity_2006;
@olivier_urbanization_2020]. Increasing, respectively decreasing, species
variability results in respectively a decrease and an increase of temporal
stability [@thibaut_understanding_2013]. Positive relationships between species
variability and species richness have been observed in experimental grasslands
[@tilman_biodiversity_2006], thereby decreasing stability. However, positive,
neutral and negative relationships have been found in natural settings
[@thibaut_understanding_2013; @olivier_urbanization_2020]. ^[Colin asked for a
word about $cv_{sp}$ and stability but my opinion is that it
is not necessary and that the depth of mecanisms are currently fairly explained
for the introduction.] Overall, positive relationships between species richness and
temporal stability are also observed in natural settings, such as stream fish communities
[@franssen_annual_2011], bird and butterfly communities
[@olivier_urbanization_2020].

---
#### Multitrophic communities
---

One has to notice that most of the empirical and experimental evidence of the
positive effect of richness on biomass production and stability through time
comes from studies focusing on one trophic level, generally primary producers or
primary consumers. Natural ecosystems generally include more than one or two
trophic levels and there is no certainty that the relationship between species
richness and total biomass and its temporal stability for a given trophic level
is representative of this relationship at the food web level. Theoretical
studies showed that food web properties, such as interaction distribution and
strength, affect the distribution of biomass among adjacent trophic levels,
[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019]. A
large body of theoretical studies links the propagation of perturbations to the
foodweb structure [@may_will_1972; @angelis_stability_1975; @dunne_network_2006;
@neutel_reconciling_2007; @duffy_why_2009; @stouffer_compartmentalization_2011],
or trophic chain [@shanafelt_stability_2018; @wang_biodiversity_2016;
@barbier_pyramids_2019]. To date, we have few evidence on the relationship
between network structure and total biomass and its temporal stability in
empirical multitrophic communities.

@@

Overall, the evidence suggests that both species richness and network structure
should modulate total biomass and stability of communities. The effects of
species richness and network structure are potentially conflicting or
synergistic in such a way that they need to be addressed jointly. Yet, there is
no direct empirical evidence to date for the combined effects of species
richness and network structure on total biomass and stability in natural
communities.

@@

When assessing the relationship between community structure and ecosystem
properties in natural communities, it is crucial to consider environmental
factors [@loreau_biodiversity_2001; @he_global_2013; @grace_integrative_2016].
Environment affects organism performance directly, and thereby, species
abundances, total biomass [@grace_integrative_2016] and temporal stability
[@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
@oliver_heterogeneous_2010; @franssen_annual_2011; @friedpetersen_drivers_2020].
For example, greater ecosystem size might increase the number of available
resources and thus total biomass [@post_ecosystem_2000; @doi_resource_2009].
@li_relationship_2018 have notably shown that climate moisture has a positive
direct effect on total biomass, but also indirect through a positive effect on
species richness. Accounting for environment also allow for an overall
comparison of the strength of the effects of environment and community
structure on total biomass and its stability.

@@

Because their trophic interactions can be infered, stream fish community
constitutes a good model to study the effects of network structure on total
biomass and its temporal stability. Despite that fish trophic
interactions are difficult to measure in natural conditions, a consequent body
of literature supports that they can be inferred through body size and diet
informations [@gravel_inferring_2013; @jennings_weak_2001;
@brose_predator_2019]. Especially in stream communities, including fishes,
@brose_predator_2019 found that the prediction of predator prey trophic
interactions based on body size ratio was far better in stream ecosystems than
in other aquatic and terrestrial ecosystems. Furthermore, the biotic activity in
stream ecosystems determines for a large part the water quality
[@cummins_structure_1974] and thus are crucial to maintain stream ecosystem
properties. Lastly, most of the diversity-biomass and diversity-stability
relationships, have been assessed in terrestrial ecosystems while there is a
evident need to test such relationships in a variety of ecosystem types.

Our study aims to document the relationships between foodweb structure and total
biomass and its temporal stability in natural communities. To do so, we used the
ONEMA dataset consisting in standardized sampling of fish communities in French
streams [@edeline_ecological_2013]. 99 sites were sampled for more than 10 years
spanning on the 1995-2018 period. We inferred 1496 interaction networks, based
on body size and food diet. We question whether species richness, connectance
and average trophic level increase, decrease or are not related to total biomass
and its temporal stability. We further question whether the species richness,
connectance and average trophic level have antagonistic or synergistic effect on
total biomass and its temporal stability. Finally, we question if 
ecosystem size and average temperature increase total biomass and its temporal
stability.

---
#We used the ONEMA dataset consisting in standardized sampling of fish
#communities in French streams [@edeline_ecological_2013]. 99 sites were sampled
#for more than 10 years spanning on the 1995-2018 period. We inferred 1496
#interaction networks, based on body size and food diet. The network structure
#was summarized by connectance and mean trophic level. Environment was
#characterized by stream size, altitude, slope, temperature, flow and enrichment.
#Finally total biomass was measured as median total biomass over the sampling
#period while its temporal stability was quantified as the inverse of the CV.
#
#We found a positive relationship between total biomass and species richness and
#network structure while total biomass and species richness had respectively a
#negative and positive effect on temporal stability. We also showed a link
#between species richness and network structure. We found that the environment had
#a strong effect on total biomass and its temporal stability in particular by 
#its effect on species richness and network structure. We then discuss the
#possible mechanisms at play to explain those results and their implications on
#our knowledge of the effect of network structure on ecosystem properties.
---

@@

## Data collection

@@

## Data preparation

The body size of all fish individuals was not recorded when they were too
numerous. The body size of the unmeasured individuals was inferred under the
assumption that species body size followed a normal distribution whose mean and
standard deviation were quantified from the recorded individuals of the sampling
(See supplementary methods, Figure S1). The body mass of each individual was
then estimated using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$
being the body mass in grams, $l$ the body size in millimeters and $i$ the
individual), where the coefficients $0.01$ and $3.03$ comes from two
meta-analyses [@lleonart_removing_2000; @froese_cube_2006]. Species biomass and
total biomass at each sampling event was then calculated by summing individual body
masses. To account for the variation in sampling effort among sites, species
biomass and total biomass have been related to the surface sampled, i.e.
$gm^{-2}$. In the further analysis, the total biomass of a station has been
defined as the median of the total biomass over time.

@@

@@

```{r}
myload(metaweb_analysis, dir= mypath("data"))
myload(trophic_class, dir= mypath("data", "classes"))
meta <- metaweb_analysis
#metaweb_analysis$resource
#meta$metaweb[meta$resource, meta$resource]
```
We determined the network structure in two steps: (1) build a metaweb describing the
trophic interactions between all trophic species and the resources (Figure
\@ref(fig:matmet) C), then (2) determine network of a given community by
subtracting the metaweb according to the trophic species present in a given
site and sampling event (Figure \@ref(fig:matmet) D).

@@

For a piscivorous trophic species, i.e. a piscivorous node, the fish-fish
trophic links was defined in two steps and based on the body size ratio between
predators and prey. First of all, the predation window of a piscivorous node was
defined as 3% to 45% of its midpoint [@mittelbach_ontogeny_1998;
@claessen_impact_2002; @hart_handbook_2008]. Then, a trophic link was set
between the piscivorous node and every node whose midpoint
was included in the predation range (Figure S2). The fish-resource trophic
links, for piscivorous and non piscivorous nodes, were set between the
trophic species and the resources nodes present in their life stage.
Lastly, the trophic links between resource nodes were set according to the food
diet data [@allan_stream_2007; @hart_handbook_2008].

For each trophic network, corresponding to a particular site and year, we
computed two of the most commonly used network metrics to characterize food
webs, namely the connectance and mean trophic level. Connectance describes 
the level of generalism in the network and is calculated as the number of actual
interaction divided by the maximum number of interaction if all species interact
together ($C = L / N^2$, L and N being resp. the number of
links and of trophic species plus resource nodes). 
The mean trophic level $\overline{T}$ was computed as the mean trophic level
weighted by the biomass of each trophic species (excluding resource nodes for
which we had no biomass information), so $\overline{T} = \sum_i^N{B_iT_i \times
\sum_i^N{B_i}^{-1}}$, with $T_i$ and $B_i$ being respectively the trophic level
and the biomass of the node $i$. The trophic level of the nodes was computed as
one added to the average trophic level of its food item.

@@

@@

## Environment

@@

The total effect of PCA2, related to average annual temperature and reversely to
altitude, on temporal stability was of higher magnitude than the effects of
species richness and mean trophic level (Table
\@ref(tab:indir-sem)).
The PCA2 had a total negative effect on temporal stability 
($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
PCA2 had an indirect positive effect on temporal stability through a
direct positive effect on $\overline{CV_{sp}}$ ($r_\delta = 
`r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)) but also a
negative on through species richness but a positive one through
mean trophic level 
(resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
$r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-sem)).
This was also true for the PCA1, related to stream size, but effects were weaker
than for PCA2.

@@

We found that species richness and mean
trophic level had a positive effect on total biomass. In contrast, species
richness had a negative effect on temporal stability whereas mean trophic level
covaried positively. Futhermore, we found that the effect of species richness
and mean trophic level on total biomass and its temporal stability were not
independant as species richness had a positive effect on mean trophic level.
Finally, we found that the magnitude of the effects of average temperature and
altitude was equal or superior to the effects of species richness and mean
trophic level. Overall, our study is unique by its level of integration, from
environmental effects to total biomass and stability, going through species
richness and network structure, and the first direct assessment of a possible
joint effect of species richness and network structure.

@@

A first step to identify the mechanisms behind those contrasting patterns is to
look at the effects of species richness on synchrony and $\overline{CV_{sp}}$.
As most studies on the topic, in experimental grasslands
[@isbell_biodiversity_2009; @roscher_identifying_2011], in natural communities
of birds, bats, grasslands, bats and butterflies [@bluthgen_land_2016;
@olivier_urbanization_2020], we found that species richness decreases synchrony,
thereby increasing stability. However, no relation has been found in
natural forests [@declerck_species_2006]. Our study thus
highlights that species richness might also decrease synchrony in empirical
trophic communities. Species richness can reduce synchrony when a given
increase in species richness leads to a decrease of population sizes, which in
turn raises the role of demographic stochasticity on population dynamics
[@loreau_species_2008] but also in the case where species have different
responses to environmental variation [@loreau_species_2008].

The positive effect of species richness on
$\overline{CV_{sp}}$, thereby decreasing stability, is more intriguing. While
positive effect of species richness on $\overline{CV_{sp}}$ was reported in
experimental grasslands and natural bird communities [@tilman_biodiversity_2006;
@olivier_urbanization_2020], negative and neutral relationships have been found
in butterfly and bat communities. However, the ecological mechanisms leading to
such relationships in foodwebs are not known and this question deserves further
research.

@@

## Mean trophic level increased total biomass and its temporal stability

The mean trophic level was positively linked to total biomass. As feeding
interactions were partly determined by body size and that body mass increase
with body size, it is expected that the more the average
biomass is located at higher trophic level, the higher the total biomass is. 
Experimental and theoretical work suggested that a
higher trophic level is the result of a stronger top-down effect, meaning higher
predation rates and biomass fluxes to higher trophic levels
[@thebault_relationship_2006; @kratina_warming_2012], hence leading to an
increase in total biomass with trophic length. Furthermore,
@wang_biodiversity_2016 have shown that total nutrient uptake might increases
with the length of trophic chain and so results in higher total biomass.

In contrast, connectance had no effect on total biomass. One might have expected
that an increase in connectance should translate in higher resource transfer
efficiency between prey and predators and so results in higher total biomass in
the fish compartment. A reason for such an absence of an effect might be due our
data lacks informations about the lower compartments of the
community, i.e, the primary producers, zooplankton and zoobenthos.

Mean trophic level had a positive effect on biomass stability by its negative
effect on $\overline{CV_{sp}}$, thereby increasing average species stability. It
might be because species at higher trophic level are more stable than the species at
lower trophic levels as predicted by food chains models [@barbier_pyramids_2019;
@shanafelt_stability_2018] but it is not sure that it holds when considering
omnivorous species [@wang_biodiversity_2016] and if other mechanisms can
generate the same pattern [@thibaut_understanding_2013]. An alternative
explanation is that higher mean trophic level leads to stronger top-down control
and resource complementarity and thus reduce biomass fluctuations in lower
trophic levels [@rooney_structural_2006; @neutel_reconciling_2007].

We found that connectance had no effect on temporal stability. This result
contradicts previous precedent theoretical studies on the relationship between
stability and network structure [@angelis_stability_1975; @may_will_1972;
@thebault_stability_2010], although they considered different stability concepts
and metrics [@arnoldi_resilience_2016]. However, our measure of connectance
suffers limitation and further research should examine
the effect of connectance on temporal stability in empirical foodwebs.

@@

Contrasting with a previous study in experimental plant communities
[@grace_integrative_2016] and in fish communities [@yvondurocher_warming_2011;
@dossena_warming_2012], we found that environmental drivers overall affect total
biomass indirectly rather than directly. In line with previous studies, we found
that the two PCA axis, respectively related to stream size and temperature, 
had indirect positive effects on total biomass, through a positive direct effect
on species richness [@allan_stream_2007; @ogorman_chapter_2012;
@emmrich_geographical_2014].

>>>>

- Number of words:
  - Abstract: 184
  - Main text: 4929

@@

Both the relations between diversity and ecosystem functioning, and between food
web complexity and stability, have received considerable attention during the
last decades in ecology. While the former relation remains rarely investigated
in the context of food webs, especially in empirical studies explicitly
considering food web structures, the latter has been mainly the focus of
theoretical studies and empirical tests are critically missing. Here we link
species richness, food web structure and total biomass and its stability by
using a dataset of standardized fish sampling in French streams running from
1995 to 2018. We inferred trophic interactions thanks to recorded body size and
diet literature. We reveal that species richness and average trophic level had a
positive relationship with total biomass of fish communities while they had
respectively a negative and positive effect on its temporal stability. We
also found that the effects of stream size and temperature on total biomass and
stability are partly mediated by their effects on diversity and food web
structure. Overall, our study opens fruitful perspectives on the link between
species richness, network structure, ecosystem properties and their stability.

@@

Species richness promotes higher biomass production in a variety of ecosystems
and taxons. Indeed species richness generally increases primary productivity and
total biomass in experimental plant communities [@tilman_productivity_1996;
@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016], but also in briophyte communities
[@mulder_physical_2001], stream feeders [@cardinale_species_2002] and aquatic
bacterial consumers [@pennekamp_biodiversity_2018]. Despite the diversity of
ecosystems and taxons studied, the relation between diversity and ecosystem
functioning remains traditionally focused on single trophic levels, ignoring the
effects of food web structure. Theoretical models have recently extended
classical theoretical studies in plant communities [@tilman_plant_1997;
@loreau_biodiversity_2001] to food webs [@thebault_food-web_2003;
@poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018].
These models show that both resource use complementarity and selection effects,
the two main mechanisms previously highlighted in single-trophic studies, are
also important to understand diversity effects in food webs
[@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
However, they also reveal new mechanisms such as positive effects of diversity
of trophic levels, i.e. associated with higher trophic levels, on ecosystem
functioning [@wang_biodiversity_2018]. Theoretical studies also showed that food
web properties, such as interaction distribution and strength, affect the
distribution of biomass among adjacent trophic levels
[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
Empirical studies are however missing to assess further how food web structure,
in conjunction with species diversity, affect total biomass production and other
ecosystem properties.

---
#### Single and multitrophic communities
---

Many studies showed that species richness also increases temporal stability of
communities, i.e. variation through time, often quantified by the temporal CV.
Such positive relationships between species richness and temporal stability have
been reported in experimental grasslands and aquatic bacterial systems
[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018] as well as in natural
settings, such as stream fish communities [@franssen_annual_2011], bird and
butterfly communities [@olivier_urbanization_2020]. However, this relation has
been mostly explored in single trophic level systems or without accounting for
food web structure, even more so than the relation between diversity and biomass
production. Single-level theoretical works have clarified which mechanisms
generate this positive relationship between species richness and temporal
stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
synchrony and (2) species variability. Species synchrony quantify to what extent
the fluctuations of abundances or biomasses through time are correlated among
species. A low synchrony in species fluctuations, i.e.  asynchrony, is
synonymous of compensatory dynamic, where the decrease in abundance of a species
is compensated by the increase of an other.  Asynchrony is generally the main
mechanism whereby species richness has a stabilizing effect on temporal
stability [@tilman_biodiversity_2006; @olivier_urbanization_2020] while
positive, neutral and negative relationships have been found in natural settings
[@tilman_biodiversity_2006; @thibaut_understanding_2013;
@olivier_urbanization_2020]. In addition to diversity, food web structure is
expected to strongly affect the stability of communities and ecosystems, as
outlined by the large body of theoretical studies on this topic [@may_will_1972;
@dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
@stouffer_compartmentalization_2011]. For instance, predation has cascading
effects on species variability [@shanafelt_stability_2018] and it affects as
well synchrony between species [@teng_dynamics_2004]. Despite a long-standing
interest on the links between food web complexity and stability in ecology, to
date we have very few evidence on the relationship between network structure and
the temporal stability of species and total biomass in empirical multitrophic
communities.

@@

Overall, the evidence suggests that both species richness and network structure
should modulate total biomass and stability of communities. The effects of
species richness and network structure, such as connectance and average trophic
level, are potentially conflicting or synergistic in such a way that they need
to be addressed jointly. Yet, there is no direct empirical evidence to date for
the combined effects of species richness and network structure on total biomass
and stability in natural communities.

Although the relationships between diversity, total biomass and its stability in
natural systems can be similar to those found in experimental communities [e.g.,
@wu_relationship_2015; @li_relationship_2018], negative or non significant
effects of species richness on total biomass have for example been found in some
natural communities such as forests [@szwagrzyk_above-ground_2007;
@jacob_productivity_2010; @seidel_relationship_2013]. Some authors suggest that
the lack of resource complementarity or environmental harshness might be
responsible for an absence or a negative effect of species richness
[@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015]. These
different relations might also arise from effects of the environment on both
diversity and ecosystem functions [@loreau_biodiversity_2001].

@@

When assessing the relationship between community structure and ecosystem
properties in natural communities, it is indeed crucial to consider
environmental factors [@loreau_biodiversity_2001; @he_global_2013;
@grace_integrative_2016]. Environment affects organism performance directly, and
thereby, species abundances, total biomass [@grace_integrative_2016] and temporal
stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
@oliver_heterogeneous_2010; @franssen_annual_2011; @friedpetersen_drivers_2020].
For example, greater ecosystem size might increase the number of available
resources and thus total biomass [@post_ecosystem_2000; @doi_resource_2009].
@li_relationship_2018 have notably shown that climate moisture has a positive
direct effect on total biomass, but also indirect through a positive effect on
species richness. Accounting for environment also allow for an overall
comparison of the strength of the effects of environment and community structure
on total biomass and its stability.

@@

Because their trophic interactions can be inferred, stream fish community
constitutes a good model to study the effects of network structure on total
biomass and its temporal stability. Despite that fish trophic
interactions are difficult to measure in natural conditions, a consequent body
of literature supports that they can be inferred through body size and diet
informations [@gravel_inferring_2013; @jennings_weak_2001;
@brose_predator_2019]. Especially in stream communities, including fishes,
@brose_predator_2019 found that the prediction of predator prey trophic
interactions based on body size ratio was far better in stream ecosystems than
in other aquatic and terrestrial ecosystems. Furthermore, the biotic activity in
stream ecosystems determines for a large part the water quality
[@cummins_structure_1974] and thus are crucial to maintain stream ecosystem
properties. Lastly, most of the diversity-biomass and diversity-stability
relationships, have been assessed in terrestrial ecosystems while there is a
evident need to test such relationships in a variety of ecosystem types.

Our study aims to document the relationships between food web structure and
total biomass and its temporal stability in natural communities. To do so, we
used the ONEMA dataset consisting in standardized sampling of fish communities
in French streams [@edeline_ecological_2013]. 99 sites were sampled for more than 10
years spanning on the 1995-2018 period. We inferred 1496 interaction networks,
based on body size and food diet. We question whether species richness,
connectance and average trophic level increase, decrease or are not related to
total biomass and its temporal stability. We further question whether the
species richness, connectance and average trophic level have antagonistic or
synergistic effect on total biomass and its temporal stability. Finally, we
question if ecosystem size and average temperature increase total biomass and
its temporal stability.

@@

## Data preparation and filtering

@@

## Variable computation

### Biomass estimation

The body size of all fish individuals was not recorded when they were too
numerous. The body size of the unmeasured individuals was inferred under the
assumption that species body size followed a normal distribution whose mean and
standard deviation were quantified from the recorded individuals of the sampling
(See supplementary methods, Figure S1). The body mass of each individual was
then estimated using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$
being the body mass in grams, $l$ the body size in millimeters and $i$ the
individual), where the coefficients $0.01$ and $3.03$ comes from two
meta-analyses on fishes [@lleonart_removing_2000; @froese_cube_2006]. Species
biomass and total biomass at each sampling event was then calculated by summing
individual body masses. To account for the variation in sampling effort among
sites, species biomass and total biomass have been related to the surface
sampled, i.e.  $gm^{-2}$. In the further analysis, the total biomass of a
station has been defined as the median of the total biomass over time.

### Stability measures

@@

### Species richness

@@

### Network building

```{r}
myload(metaweb_analysis, dir= mypath("data"))
myload(trophic_class, dir= mypath("data", "classes"))
meta <- metaweb_analysis
#metaweb_analysis$resource
#meta$metaweb[meta$resource, meta$resource]
```

We determined the network structure in two steps: (1) build a metaweb describing the
trophic interactions between all trophic species and the resources (Figure
\@ref(fig:matmet) C), then (2) determine network of a given community by
subtracting the metaweb according to the trophic species present in a given
site and sampling event (Figure \@ref(fig:matmet) D).

@@

For a piscivorous trophic species, i.e. a piscivorous node, the fish-fish
trophic links was defined in two steps and based on the body size ratio between
predators and prey. First of all, the predation window of a piscivorous node was
defined as 3% to 45% of its midpoint [@mittelbach_ontogeny_1998;
@claessen_impact_2002; @hart_handbook_2008]. Then, a trophic link was set
between the piscivorous node and every node whose midpoint
was included in the predation range (Figure S2). The fish-resource trophic
links were set between the trophic species and the resources nodes according the
food diet of their size class, for both the piscivorous and non piscivorous
trophic species. Lastly, the trophic links between resource nodes were set
according to the food diet data [@allan_stream_2007; @hart_handbook_2008].

### Network structure

For each trophic network, corresponding to a particular site and year, we
computed two of the most commonly used network metrics to characterize food
webs, namely the connectance and mean trophic level. 
As the networks, the networks metrics were also based on the trophic species,
i.e. body size classes. Connectance describes the level of generalism in the
network and is calculated as the number of actual
interaction divided by the maximum number of interaction if all species interact
together ($C = L / N^2$, L and N being resp. the number of links and of trophic
species plus resource nodes). The mean trophic level $\overline{T}$ was computed
as the mean trophic level weighted by the biomass of each trophic species
(excluding resource nodes for which we had no biomass information), so
$\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and
$B_i$ being respectively the trophic level and the biomass of the node $i$. The
trophic level of the nodes was computed as one added to the average trophic
level of its food item. For each site, the median of connectance and average
trophic level over time was used in subsequent analysis.

@@

mysave(habitat_press, habitat_pressure, dir = mypath("data"))

@@

## Environmental variables

@@

The total effect of PCA2, related to average annual temperature and reversely to
altitude, on temporal stability was of higher magnitude than the effects of
species richness and mean trophic level (Table
\@ref(tab:indir-sem)).
The PCA2 had a total negative effect on temporal stability, meaning that higher
temperature results in lower stability
($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
PCA2 had an indirect positive effect on temporal stability through a
direct positive effect on $\overline{CV_{sp}}$ ($r_\delta = 
`r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)) but also a
negative on through species richness but a positive one through
mean trophic level
(resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
$r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-sem)).
This was also true for the PCA1, related to stream size, but effects were weaker
than for PCA2.

@@

Overall, our study is unique by its level of integration, from environmental
effects to total biomass and stability, going through species richness and
network structure, and the first direct assessment of a possible joint effect of
species richness and network structure.  We found that species richness and mean
trophic level had a positive effect on total biomass. In contrast, species
richness had a negative effect on temporal stability whereas mean trophic level
covaried positively. We also found that the effect of species richness and mean
trophic level on total biomass and its temporal stability were not independant
as species richness had a negative effect on mean trophic level.  Furthermore,
we found that connectance had no significant effect on both total biomass and
its temporal stability. Finally, we found that the magnitude of the effects of
average temperature and altitude was equal or superior to the effects of species
richness and mean trophic level.

@@

A first step to identify the mechanisms behind those contrasting patterns is to
look at the effects of species richness on synchrony and $\overline{CV_{sp}}$.
As most studies on the topic, in experimental grasslands
[@isbell_biodiversity_2009; @roscher_identifying_2011], in natural communities
of birds, bats, grasslands, bats and butterflies [@bluthgen_land_2016;
@olivier_urbanization_2020], we found that species richness decreases synchrony,
thereby increasing stability [but see @declerck_species_2006]. Our study thus
highlights that species richness might also decrease synchrony in empirical
trophic communities. Species richness can reduce synchrony when a given
increase in species richness leads to a decrease of population sizes but also in
the case where species have different responses to environmental variation
[@loreau_species_2008].

The positive effect of species richness on
$\overline{CV_{sp}}$, thereby decreasing stability, is more intriguing. While
positive effect of species richness on $\overline{CV_{sp}}$ was reported in
experimental grasslands and natural bird communities [@tilman_biodiversity_2006;
@olivier_urbanization_2020], negative and neutral relationships have been found
in butterfly and bat communities. ** Our results contrast with a previous
meta-analysis which concludes that species richness had a positive effect on
population stability in multi-trophic aquatic microcosms
[@jiang_different_2009]. In foodwebs, the relationship between temporal
stability of populations and species richness depends on interaction strength
and their distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
@brose_allometric_2006], high interaction strength inducing a negative
relationship. Overall, more research is needed to assess the links between
species richness and the functioning of empirical foodwebs.**

@@

## Average trophic level increased total biomass and its temporal stability

The average trophic level was positively linked to total biomass.
Experimental and theoretical work suggested that a higher trophic level is the
result of a stronger top-down effect, meaning higher predation rates and biomass
fluxes to higher trophic levels [@kratina_warming_2012], hence leading to an
increase in total biomass with trophic length. Furthermore,
@wang_biodiversity_2016 have shown that total nutrient uptake might increases
with the length of trophic chain and so results in higher total biomass.

In contrast, connectance had no effect on total biomass. One might have expected
that an increase in connectance may translate in higher total nutrient uptake
and so results in higher total biomass in the fish compartment. A reason for
such an absence of an effect might be due our data lacks informations about the
lower compartments of the community, i.e, the primary producers, zooplankton and
zoobenthos.

Mean trophic level had a positive effect on biomass stability by its negative
effect on $\overline{CV_{sp}}$, thereby increasing average species stability. It
might be because species at higher trophic level are more stable than the species at
lower trophic levels as predicted by food chains models [@barbier_pyramids_2019;
@shanafelt_stability_2018] but it is not sure that it holds when considering
omnivorous species [@wang_biodiversity_2016]. An alternative explanation is that
higher mean trophic level leads to stronger top-down control and resource
complementarity and thus reduce biomass fluctuations in lower trophic levels
[@rooney_structural_2006].

We found that connectance had no effect on temporal stability. This result
contradicts previous precedent theoretical studies on the relationship between
stability and network structure [@angelis_stability_1975; @may_will_1972;
@thebault_stability_2010; but see @neutel_reconciling_2007], although they
considered different stability concepts and metrics [@arnoldi_resilience_2016].
However, our measure of connectance suffers limitation (discussed above) and
further research should examine the effect of connectance on temporal stability
in more complete empirical foodwebs.

## Population stability was the main driver of temporal stability

**It was unexpected that the average population variability ($\overline{CV_{sp}}$) had a
stronger negative effect on biomass stability than synchrony
[@bluthgen_land_2016; @olivier_urbanization_2020], and explain why we observe a
negative effect of species richness on temporal stability of biomass. The lower
effect of synchrony might be explained by the presence of generalist predators in
stream communities, which can raise synchrony between prey species which shares
the same predator [@raimondo_interspecific_2004]. In the other way, it is
possible that, in aquatic foodwebs, the occurrence of large oscillatory dynamics
[@mccann_reevaluating_1997] leads to a higher contribution of population
variability rather than synchrony to community stability. How both
strengths and the relative contribution of synchrony and population
variaribility to overall stability vary between foodwebs and single trophic communities is
still an open question.**

---
#Rough average synchrony in Théophile study: exp(-0.75) = .47 or exp(-0.6) = .54
#This study: sync avg = .69
---

@@

**We found that the total effect of environmental drivers on total biomass and its
stability was indirect and of the same magnitude order than the effect of
species richness and average trophic level, highlighting that environmental
changes may result in signicant ecosystem responses, through alteration of
both species richness and network structure.**

Consistent with research showing that food webs in wider streams, are also
larger, and hence support more species and biomass [@allan_stream_2007], we
found that the PCA axis related to stream size had a positive effect on total
biomass through a positive effect on mean trophic level. Greater ecosystem size
might provide a greater diversity of resources through habitat heterogeneity,
and so higher species richness and total biomass by surface unit, through
resource complementarity. Greater diversity of resources can also maintain
more biomass at high trophic level [@post_ecosystem_2000; @doi_resource_2009].
Furthermore, the positive effect of the PCA axis related to temperature on total
biomass was of the magnitude of effects of network structure and species
richness, in line with the mounting body of work reporting important effects of
temperature on the structure and biomass of aquatic system [e.g.
@dossena_warming_2012; @edeline_ecological_2013; @emmrich_geographical_2014;
@hattab_forecasting_2016]. Contrasting with a previous study in experimental
plant communities [@grace_integrative_2016] and in fish communities
[@yvondurocher_warming_2011; @dossena_warming_2012], we found that environmental
drivers overall affect total biomass indirectly rather than directly.
